%\bibliographystyle{unsrt}
%\bibliography{bibliography}

\begin{thebibliography}{90}

  \bibitem[BF01]{bf}  Dan Boneh and Matthew K. Franklin. Identity-based encryption from the weil pairing. In {\em CRYPTO}, volume 2139 of {\em Lecture Notes in Computer Science}, pages 213-229, 2001.
  
  \bibitem[BLR$^+$15]{blr}  Dan Boneh and Kevin Lewi and Mariana Raykova and Amit Sahai and Mark Zhandry and Joe Zimmerman.  Semantically Secure Order-Revealing Encryption: Multi-Input Functional Encryption Without Obfuscation. EUROCRYPT 2015.
  
    \bibitem[BS03]{bs} Dan Boneh and Alice Silverberg. Applications of multilinear forms to cryptography. {\em Contemporary Mathematics}, 324:71?90, 2003.
    
    \bibitem[BWZ14]{bwz} Dan Boneh, David J. Wu, and Joe Zimmerman. Immunizing multilinear maps against zeroizing attacks. Cryptology ePrint Archive, Report 2014/930, 2014. http://eprint.iacr.org/.
    
    \bibitem[CGH$^+$15]{cgh} Jean-Sebastien Coron and Craig Gentry and Shai Halevi and Tancrede Lepoint and Hemanta K. Maji and Eric Miles and Mariana Raykova and Amit Sahai and Mehdi Tibouchi. Zeroizing Without Low-Level Zeroes: New MMAP Attacks and Their Limitations. Cryptology ePrint Archive, Report 2015/596, 2015. http://eprint.iacr.org/.  To appear at CRYPTO 2015.
    
      \bibitem[CHL$^+$14]{chl} Jung Hee Cheon, Kyoohyung Han, Changmin Lee, Hansol Ryu, Damien Stehlé. Cryptanalysis of the multilinear maps over the integers. Cryptology ePrint Archive, Report 2014/906, 2014. http://eprint.iacr.org/.  To appear at EUROCRYPT 2015.

  \bibitem[CLT13]{clt} Jean-Sebastien Coron, Tancrede Lepoint, and Mehdi Tibouchi. Practical multilinear maps over the integers. In {\em CRYPTO}, pages 476-493, 2013.
  
  \bibitem[CLT14]{clt14} Jean-Sébastien Coron, Tancréde Lepoint, and Mehdi Tibouchi. Cryptanalysis of two candidate fixes of multilinear maps over the integers. Cryptology ePrint Archive, Report 2014/975, 2014. http://eprint.iacr.org/.
  
  \bibitem[CLT15]{clt15} Jean-Sébastien Coron, Tancréde Lepoint, and Mehdi Tibouchi. New multilinear maps over the integers. In R. Gennaro and M. Robshaw, editors, CRYPTO 2015, Lecture Notes in Computer Science. Springer, 2015. To appear.

  \bibitem[GGH13a]{ggh13a}  Sanjam Garg, Craig Gentry, and Shai Halevi. Candidate multilinear maps from ideal lattices. In {\em EUROCRYPT 2013}. Springer Berlin Heidelberg, 2013.

  \bibitem[GGH$^+$13b]{ggh13b} Sanjam Garg, Craig Gentry, Shai Halevi, Mariana Raykova, Amit Sahai, and Brent Waters. Candidate indistinguishability obfuscation and functional encryption for all circuits. Cryptology ePrint Archive, Report 2013/451, 2013. http://eprint.iacr.org/.
  
    \bibitem[GGH14a]{ggh14a} Craig Gentry, Sergey Gorbunov, and Shai Halevi. Graph-induced multilinear maps from lattices. Cryptology ePrint Archive, 2014:645, 2014. To appear at TCC 2015.
  
  \bibitem[GGH$^+$14b]{ggh14b} Craig Gentry, Shai Halevi, Hemanta K. Maji, and Amit Sahai. Zeroizing without zeroes: Cryptanalyzing multilinear maps without encodings of zero. Cryptology ePrint Archive, Report 2014/929, 2014. http://eprint.iacr.org/.
  
  \bibitem[GSW13]{gsw}  Craig Gentry, Amit Sahai, and Brent Waters. Homomorphic Encryption from Learning with Errors: Conceptually-Simpler, Asymptotically-Faster, Attribute-Based. In Advances in Cryptology---CRYPTO 2013, R. Canetti and J. Garay, Eds., vol. 8042 of Lecture Notes in Computer Science. Springer Berlin Heidelberg, 2013, pp. 75-92.
  
  \bibitem[HJ15]{hj} Y. Hu and H. Jia. Cryptanalysis of GGH map. Cryptology ePrint Archive, Report 2015/301,
2015. http://eprint.iacr.org/.

  \bibitem[Reg05]{reg05} On lattices, learning with errors, random linear codes, and cryptography. In \emph{STOC}, pages 84-93, 2005.


  \end{thebibliography}