\section{Our construction}

We are now ready to outline our map, which is an instantiation of a graded encoding scheme as in prior works \cite{clt, ggh13a, clt15}.  The basic operations (setup, encoding, addition, multiplication) of our scheme are essentially identical to those of the GSW scheme.

In general, a fresh encoding of a plaintext $\mu \in \Rq$ at level-$i$ will look like the following, $z$ is a random ring element, $T$ is a uniform matrix, and $A$ is a GSW public key:
$$C' = z^{-i}T C T^{-1}$$
where $C$ is a GSW encoding of $\mu$.  That is, $$C = \flattenfn\left(\mu I_{N} + \bdfn(R\cdot A))\right)$$ where $R \leftarrow \{0,1\}^{N\times m}$. Encodings are simply GSW ciphertexts (which are small, as they are a result of the $\flattenfn$ function) pre/post-multiplied by a randomization matrix $T$ and its inverse and by the ring element $z^{-i}$ to introduce the notion of levels (and we work over a polynomial ring instead of the integers).

\paragraph{Setup: $(\mathsf{pp},\pzt) \leftarrow \mathsf{setup}(1^\lambda, 1^\kappa)$.}  Given the security parameter $\lambda$ and the multilinearity level $\kappa$, we generate the public parameters and the zero-testing element.  The parameters $q$ and $n$ define the ring $\Rq$.  Set $m = O(\log q)$ and $N = 2\ell$ where $\ell = \lceil \log q \rceil$.  Let $\chi$ be an error distribution on $\Rq$.  $\sigma$ is a parameter for sampling plaintext elements from a discrete Gaussian distribution.  We generate the {\bf encoding key} $A$ by drawing $\vec{e} \leftarrow \chi^m$, $\vec{a} \leftarrow \Rq^m$, and $t \leftarrow \Rq$.  Set $\vec{b} = \vec{a}t + \vec{e}$ and $\vec{s} = (1, -t)^T$ and $A = \big(\vec{b} \; \big| \; \vec{a}\big)$.  We generate the {\bf zero-testing parameter} $\pzt$ by first drawing uniform matrices $U \leftarrow \Rq^{N\times 2}$ and $T \leftarrow \Rq^{N \times N}$ and setting $$S = \bdfn(U)\cdot T^{-1}$$  Then draw a uniform element $z \leftarrow \Rq$ and then a few ``somewhat small" elements $\alpha \leftarrow \mathcal{D}_{\mathbb{Z}^n, \sigma_\alpha}$, $\vec{\epsilon} \leftarrow (\mathcal{D}_{\mathbb{Z}^n, \sigma_\delta})^N$, and $\vec{\delta} \leftarrow (\mathcal{D}_{\mathbb{Z}^n, \sigma_\epsilon})^N$ for some parameters $\sigma_\alpha, \sigma_\delta,$ and $\sigma_\epsilon$.  We then set $$\p = z^\kappa T\cdot (\alpha(\vec{v} + \vec{\delta}) + \vec{\epsilon})$$ where $\vec{v} =  \powfn(\vec{s})$.  Intuitively, $\p$ is a vector of $N$ RLWE ``encryptions" of the $N$ coefficients of $\vec{v}$, the original decryption key in GSW.  We generate a level-1 encoding $Y$ by drawing $R \leftarrow \{0,1\}^{N\times m}$ and setting $$Y = T\cdot\flattenfn(I_N + \bdfn(R\cdot A))\cdot T^{-1}$$  which is a level-1 encoding of 1. We generate the rerandomization parameters $X_i$ by drawing $R_i \leftarrow \{0,1\}^{N \times m}$ and setting $$X_i = z^{-i}T\cdot\flattenfn(\bdfn(R_i\cdot A))\cdot T^{-1}$$ for $1 \leq i \leq \tau$.  Note that these are level-1 encodings of 0. We output $\mathsf{pp} = (\kappa, q,n,m,N,\sigma, Y, \{X_i\}_{i=1}^\tau)$, $P$, and $\pzt = (S,\p)$.

\paragraph{Zero testing:  $\mathsf{isZero}(C', \pzt) \stackrel{?}{=} 0/1$.}  To zero-test a (fresh) encoding $C' = z^{-\kappa} T C T^{-1}$ of $\mu$ at level-$\kappa$, compute $\vec{w} = S\cdot C\cdot \p$ and output 1 if $||\vec{w}|| < P$ and 0 otherwise.  To see why this is correct, note that we have:  $$A\vec{s} = \vec{b} - \vec{a}t = \vec{e}$$  Thus, $\bdfn(A)\vec{v} = \vec{e}$ as $\vec{v} = \powfn(\vec{s})$.  Additionally, $\flattenfn(C)\cdot\powfn(\vec{s}) = C\cdot \powfn(\vec{s}) = C\cdot\vec{v}$, so we have:
\begin{align*}
S\cdot C'\cdot \p &= S \cdot z^{-\kappa} T C T^{-1} \cdot \p \\
&= z^{-\kappa} ST C  T^{-1} \cdot z^\kappa T\cdot (\alpha(z^\kappa\vec{v} + \vec{\delta}) + \vec{\epsilon})\\
&= (z^{-\kappa} z^{\kappa}) ST \cdot C (\alpha(\vec{v} + \vec{\delta}) + \vec{\epsilon})\\
&= ST \cdot (\alpha(C\vec{v} + C\vec{\delta}) + C\vec{\epsilon})\\
&= ST \cdot (\alpha((\mu I_{N} + \bdfn(R\cdot A)))\vec{v} + C\vec{\delta}) + C\vec{\epsilon})\\
&= ST \cdot (\alpha((\mu \vec{v} + \vec{e})) + C\vec{\delta}) + C\vec{\epsilon})\\
&= \bdfn(U)T^{-1}\cdot T \cdot (\alpha((\mu \vec{v} + \vec{e})) + C\vec{\delta}) + C\vec{\epsilon})\\
&= \bdfn(U) \cdot (\alpha((\mu \vec{v} + \vec{e})) + C\vec{\delta}) + C\vec{\epsilon})\\
&= \alpha((\mu U \vec{v} + \bdfn(U)\vec{e}) + \bdfn(U)\cdot C\vec{\delta}) + \bdfn(U)\cdot C\vec{\epsilon}\\
\end{align*} 
Intuitively, note that this element is large if and only if $\mu \not= 0$ because all elements are small except for $\vec{v}$ and $U$.  Formally, we prove the following lemma in the appendix.

\begin{lemma}
\label{zerotesting}
This is the lemma that formally outlines the size difference between a zero and nonzero encoding (informally stated for now).  Let $C' = z^{-\kappa} TCT^{-1}$ where $C$ is a GSW ciphertext of a plaintext $\mu \in \Rq$ (i.e., $C\vec{v}$ decrypts to $\mu$).  Then $\norm{\infty}{S\cdot C' \cdot \p} < P$ if and only if $\mu = 0$.
\end{lemma}

\paragraph{Addition \& subtraction.}  For two encodings $C'_1$ and $C'_2$ at the same level-$i$, addition and subtraction are the corresponding matrix operations.  We demonstrate the correctness of these operations with addition; subtraction follows immediately.  Suppose that the encodings $C'_1$ and $C'_2$ have corresponding GSW ciphertexts $C_1$ and $C_2$ of plaintexts $\mu_1$ and $\mu_2$.  Then:
\begin{align*}
(C_1 + C_2)\vec{v} &= C_1\vec{v} + C_2\vec{v}\\
&= (\mu_1 \vec{v} + \vec{e_1}) + (\mu_2 \vec{v} + \vec{e_2})\\
&= (\mu_1 + \mu_2)\vec{v} + \vec{e'}
\end{align*}
Thus, $C_1+ C_2$ is a valid GSW ciphertext of $\mu_1 + \mu_2$, so the correctness with respect to zero-testing for $C'_1 + C'_2$ follows from Lemma \ref{zerotesting}.

\paragraph{Multiplication.}  Multiplication is also matrix multiplication.  Suppose that $C'_1$ and $C'_2$ are encodings at level-$i$ and level-$j$, respectively, with $i+j \leq \kappa$ and corresponding GSW ciphertexts $C_1$ and $C_2$.  First note that
\begin{align*}
C'_1\cdot C'_2 &= (z^{-i}TC_1T^{-1})\cdot(z^{-j}TC_2T^{-1})\\
&= z^{-i-j}T(C_1\cdot C_2)T^{-1}
\end{align*}
We now simply need to prove that $C_1 \cdot C_2$ correctly decrypts in GSW and the result follows as before:
\begin{align*}
(C_1\cdot C_2)\vec{v} &= C_1(\mu_2 \vec{v} + \vec{e_2}) \\
&= \mu_1\mu_2\vec{v} + \mu_2\vec{e_1} + C_1\vec{e_2}
\end{align*}
which properly decrypts $\mu_1\mu_2$ in GSW if $\mu_2$ is small---for this reason our message space is restricted, as in CLT and GGH (to control noise growth).

\paragraph{Sampling:  $\mu \leftarrow \mathsf{samp}(\mathsf{pp})$.}  To sample a level-0 encoding---that is, a plaintext element---simply draw $\mu\leftarrow \mathcal{D}_{\mathbb{Z}^n, \sigma}$.

\paragraph{Rerandomization: $C' \leftarrow \mathsf{rerand}(\mathsf{pp}, C)$.}  To rerandomize a level-1 encoding $C$, draw $r_j \leftarrow \{0,1\}$ for $0 \leq j \leq \tau$ and compute $$C' = C + \sum_{j=1}^\tau r_jX_j$$ using the addition operator of the scheme.

\paragraph{Encoding:  $C \leftarrow \mathsf{enc}(\mathsf{pp},U,i)$.}  A user can encode a plaintext $\mu$ to level-$i$ by first computing $Y' \leftarrow \mathsf{rerand}(\mathsf{pp}, Y)$, which will be a rerandomized level-1 encoding of 1, and then setting $$C = \mu \cdot \left(Y'\right)^i$$ using the multiplication operator of the scheme, which will be a level-$i$ encoding of $\mu$.

\paragraph{Extraction: $sk \leftarrow \mathsf{ext}(\mathsf{pp}, \pzt, C^{(\kappa)})$.}  As in \cite{ggh13a, clt15} we apply the zero-tester to a level-$\kappa$ encoding $C^{(\kappa)}$ and collect the most significant bits to extract a random function of the underlying plaintext $\mu$.

\begin{lemma}
\label{extraction}
This is the lemma that states we can extract a random function of $\lambda$ bits from a level-$\kappa$ encoding.
\end{lemma}





\subsection{Asymmetric variants}

As in CLT and GGH we can instead compute $z_i$ for $i \in [\kappa]$ and encode plaintexts to specific index sets $S \subseteq [\kappa]$ rather than levels.  This is required for some applications like obfuscation.  We can also break the commutativity of the scheme and enforce a particular order of multiplication by generating many matrices $T_i$ rather than a single matrix $T$.

\subsection{Setting parameters}

As in homomorphic encryption schemes and multilinear maps, the size of the noise at level-$\kappa$ is dependent on the size of the initial error $B_e$, the multilinearity level $\kappa$, and the initial size of plaintexts $B_\mu$.  Specifically, we have the noise bounded by:
\begin{equation}
\label{noise1}
B_\kappa = (nN\cdot B_\mu)^\kappa \cdot B_e
\end{equation}

Then, when we apply the zero-testing element at level-$\kappa$ we have:
\begin{equation}
\label{noise2}
C\pzt = \alpha (\mu \vec{v} + \vec{e_{\circ}} + C\vec{\delta}) + C\vec{\epsilon}
\end{equation}
where the size of $e_{\circ}$ is bounded by $B_\kappa$, as in \eqref{noise1}.  In the case of $\mu = 0$ we then have the size of \eqref{noise2} bounded by $B_\alpha(B_\kappa + nNB_\delta) + nNB_\epsilon$.

\paragraph{Parameters that need to be set.}

\begin{itemize}
\item $n$, the degree of polynomials.  Dependent on RLWE security.
\item $q$, the size of the underlying field.  Dependent on RLWE security and (more importantly) the size of zero-tested elements, which depends on $n, N, \chi, \kappa, \sigma, \sigma_\alpha, \sigma_\delta, \sigma_\epsilon$.
\item $\sigma$, the parameter for the Gaussian that samples plaintexts.  GGH bounds the size of their ciphertexts (not their plaintexts by $q^{1/8}$).
\item $\sigma_\alpha, \sigma_\delta, \sigma_\epsilon$, the parameters for the Gaussians that draw noise elements for the zero-tester.  GGH sets $\sigma_\alpha$ to be $\sqrt{q}$.  Should be ``as large as possible" but obviously cannot yield a uniform distribution.
\item $\chi$, the error distribution for the RLWE instance $A$.
\item $\tau$, the number of encodings of $0$ we publish for rerandomization.
\end{itemize}


